---
title: "NotesS4"
author: "Andrew Wang"
date: "2024-01-18"
output: pdf_document
---

```{r setup, include=FALSE}
# clean up and setup
rm(list=ls()) # clean up any old stuff in R

library(tidyverse)
library(dplyr)
library(lubridate)
library(ggplot2)
library(zoo)

setwd("C:/Users/hyper/OneDrive/Documents/GitHub/Insurance-Corporate-Bonds")

df <- readRDS('insurers_transactions.rds')
brokers <- read.csv('brokers.csv')
```

## Summary

This document outlines my methodology and implementation for calculating the HHI index in alignment with step 4 of the notes document. 

First, we conduct basic filtering and feature engineering to extract a quarter and year pair for grouping
```{r cars}
#Basic filtering conducted on the read-in data 
df <- df[df$trade_cost > 0, ]
df$quarter <- quarters(df$report_date)
df$year <- year(df$report_date)
df$Time <- as.yearqtr(paste(df$year, df$quarter))
```


I implemented the following function to take in a filtered dataframe and return a table consisting of quarters and years in one column and the associated HHI index value for the time period in the other column. We want to calculate volume by broker, so we group by two variables and sum the transaction amounts. We then want some macro data about the set, in which we calculate N and total volume. We merge this back into the dataset to provide a basis for calculating s, which is the squared proportion of broker volume over total volume. We then group by time again and calculate the indexes for each period, before returning the output. 
```{r pressure}
makeHHI <- function(df) {
  df$trns_amount <- abs(df$trns_amount)
  hhi1 <- df %>% group_by(Time, brok_id) %>% transmute(
    vol = sum(trns_amount)
  ) %>% as.data.frame() %>% unique() 
  
  hhi1Meta <- hhi1 %>% group_by(Time) %>% transmute(
    num = n(), 
    quartVol = sum(vol)
  ) %>% as.data.frame() %>% unique()
  hhi1 <- merge(hhi1, hhi1Meta, all.x = TRUE)
  hhi1$s <- (hhi1$vol / hhi1$quartVol)^2
  hhi1 <- hhi1 %>% group_by(Time) %>% transmute(
    index = (sum(s) - (1/num)) / (1 - 1/num)
  ) %>% as.data.frame() %>% unique()
  return(hhi1)
}
```

We apply this function to both the (i) and (ii) calculations, while we use an altered version for demand side concentration for (iii)
```{r sp2}

#4.1 among dealers only - grouping brok_id
subset <- df %>% filter(elec_platf == 0) %>% filter(ATS == 0)
hhi1 <- makeHHI(subset)

#4.2 among dealers and ep/ats
hhi2 <- makeHHI(df)

#4.3 among investors 
hhi3 <- df %>% group_by(Time, fund_id) %>% transmute(
  vol = sum(trns_amount)
) %>% as.data.frame() %>% unique() 

hhi3Meta <- hhi3 %>% group_by(Time) %>% transmute(
  num = n(), 
  quartVol = sum(vol)
) %>% as.data.frame() %>% unique()
hhi3 <- merge(hhi3, hhi3Meta, all.x = TRUE)
hhi3$s <- (hhi3$vol / hhi3$quartVol)^2
hhi3 <- hhi3 %>% group_by(Time) %>% transmute(
  index = (sum(s) - (1/num)) / (1 - 1/num)
) %>% as.data.frame() %>% unique()
```

```{r sp3}
hhi1$i <- hhi1$index
hhi1$index <- NULL
hhi2$ii <- hhi2$index
hhi2$index <- NULL
hhi3$iii <- hhi3$index
hhi3$index <- NULL
out <- merge(hhi1, hhi2)
out <- merge(out, hhi3)

out2 <- out %>%
  pivot_longer(c(i, ii, iii)) 

ggplot(out2, aes(Time, value, color = name)) + geom_point() + geom_line() + scale_x_yearqtr() + ggtitle("HHI indexes by quarter") + ylab("Proportion")
print(out)
```
At the end we perform some basic merging functions to get the aggregate dataset. 