---
title: "VariableExitTimelines"
author: "Andrew Wang"
date: "2024-01-04"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# clean up and setup
rm(list=ls()) # clean up any old stuff in R

library(tidyverse)
library(dplyr)
library(lubridate)

setwd("C:/Users/hyper/OneDrive/Documents/GitHub/Insurance-Corporate-Bonds")
#setwd("/home/fnce/wangchj/projects/chj_projects/data/corpBond")

df <- readRDS('insurers_transactions.rds')
brokers <- read.csv('brokers.csv')
```

## Method

We wish to determine whether a company has had a time-based gap of a certain size in their trading history. To do this, we group all observations by company and calculate the elapsed time between observations. As we are only interested in specific companies on a time basis, we can just take the maximum of elapsed time. The code below performs this operation. 

```{r cars}
#Basic filtering conducted on the read-in data 
df <- df[df$trade_cost > 0, ]

df <- df %>% group_by(parent_id) %>% arrange(report_date, .by_group = TRUE) %>% mutate(
  diff = day(days(report_date - lag(report_date, default = report_date[1], order_by = report_date)))
)

#TODO: Not sure if this is correct because it assumes only one ob of interest 
#TODO: May also want to change evaluate metrics to be lower-bounded (i.e >= 2 months but <= 6 months)
df <- df %>% group_by(parent_id) %>% summarize(
  maxDist = days(max(diff))
) %>% as.data.frame()
```

## Output
We calculate the exit timelines of interest using multiple options for maximum distance, and output them below: 

```{r pressure, echo=FALSE}
month1 <- df[df$maxDist >= months(1), ]
month2 <- month1[month1$maxDist >= months(2), ]
quarter <- month2[month2$maxDist >= months(3), ]
halfyear <- quarter[quarter$maxDist >= months(6), ]
year1 <- halfyear[halfyear$maxDist >= years(1), ]
year2 <- year1[year1$maxDist >= years(2), ]
year5 <- year2[year2$maxDist >= years(5), ]
decade <- year5[year5$maxDist >= years(10), ]
summary(df$maxDist)
#output
print(paste("Number of companies with at least a 1 month gap: ", toString(dim(month1)[1])))
print(paste("Number of companies with at least a 2 month gap: ", toString(dim(month2)[1])))
print(paste("Number of companies with at least a 3 month gap: ", toString(dim(quarter)[1])))
print(paste("Number of companies with at least a 6 month gap: ", toString(dim(halfyear)[1])))
print(paste("Number of companies with at least a 1 year gap: ", toString(dim(year1)[1])))
print(paste("Number of companies with at least a 2 year gap: ", toString(dim(year2)[1])))
print(paste("Number of companies with at least a 5 year gap: ", toString(dim(year5)[1])))
print(paste("Number of companies with at least a 10 year gap: ", toString(dim(decade)[1])))
```


